Sharing displays and data from vision science research with Databrary

### 2015-05-03 vss-15/poster.tex
small edits

					Applicants promise to uphold ethical principles and sign an access agreement. The institution co-signs the agreement.

@@

					Identifiable data may only be shared if participants have given permisssion.

@@

			Video and audio data are transcoded into standard and HTML5-compatible formats, currently H.264+AAC as MP4. Databrary stores other data in native formats (e.g., .doc, .docx, .xls, .xlsx, .txt, .csv, .pdf, .jpg, .png).

@@

			Data are preserved indefinitely in a secure data storage facility at NYU managed by the university's central information technologies organization. Central IT staff handle storage, network, and backup systems. NYU does routine tape backups that are stored off site. There is no cost to use the system; an institutional subscription model is under development.

@@

			Databrary's splash page shows a timeline of recent activity, a set of clickable tags that link to studies with those search terms, a featured dataset, and links that enable users to search for data or manage their own data.

@@

			Users may upload video and related data \emph{as they collect it}, recording information about individual data collection sessions such as participant characteristics, sharing permission levels, and study conditions. 

>>>>

					Applicants promise to uphold ethical principles and sign an access agreement. The institution co-signs the agreement to grant authorization.

@@

					Identifiable data may only be shared if participants have given informed consent.

@@

			Video data are transcoded into standard and HTML5-compatible formats, currently H.264+AAC as MP4. Databrary stores other data in native formats (e.g., .doc, .docx, .xls, .xlsx, .txt, .csv, .pdf, .jpg, .png).

@@

			Data are preserved indefinitely in a secure data storage facility at NYU managed by the university's central information technologies organization. Central IT staff handle storage, network, and backup systems. NYU does routine tape backups that are stored off site. There is no cost to use the system.

@@

			Databrary's splash page shows a feed of recent activity, a set of clickable tags that link to studies with those search terms, a featured dataset, and links that enable users to search for data or manage their own data.

@@

			Users may upload video and related data \emph{as they collect it}, recording information about individual data collection sessions such as participant characteristics, sharing permission levels, and study conditions. Once uploaded, the project remains private only to named collaborators until the data owner chooses to share it with Databrary. 
